---
title: "Custom Report from History"
author: "Bernd Jagla"
date: "1/20/2020"
output: html_document
---


# history files

intro to history file organization and it procedure.

TODO: addin to remove files not needed anymore for a given active document (check load statements vs. files available and either list files or remove them, or move them.)

TODO: optional integration of shiny elements / modules

Basic information is already provided in the history. Here we just show how to create specific plots/tables.

# not yet in implemented but should be


```{r}
sampNames <- levels(colData(scEx)$sampleNames)
sampleCols=list()
sampleCols$colPal <- allowedColors[seq_along(sampNames)]
```

```{r}
source("../../inst/app/contributions/sCA_subClusterAnalysis/reactives.R")
```


# individual plots

## histogram raw counts

```{r histogram raw counts}
dat <- data.frame(counts = Matrix::colSums(assays(scEx)[["counts"]]))
dat$sample <- colData(scEx)$sampleNames
scols <- sampleCols$colPal
retVal <- ggplot(data = dat, aes(counts, fill = sample)) +
  geom_histogram(bins = 50) +
  labs(title = "Histogram for raw counts", x = "count", y = "Frequency") +
  scale_fill_manual(values = scols, aesthetics = "fill")
retVal
```


## sample info

```{r sampleInfo}
samples = colData(scEx)$sampleNames
counts <- table(samples)
df <- as.data.frame(counts)
ggplot(data = df,aes(x=samples, y=Freq, fill=samples)) + geom_bar(stat = "identity")  + 
  scale_color_manual(values=scols) 
```


## Violin Plot

```{r}
source("../../inst/app/contributions/coE_coExpression//reactives.R")
```


```{r violin}
  geneListStr <- c("PDCD1")
  projectionVar <- "dbCluster"
  minExpr <- 1
  coE_showPermutations <- FALSE
  # colPal = coE_geneGrp_vioFunc # TODO must be wrong
  # sampCol <- sampleCols$colPal
ccols <- allowedColors[1:length(levels(projections$dbCluster))]
  upI <- coE_updateInputXviolinPlot() # no need to check because this is done in projections
  if (is.null(projections) | is.null(scEx_log)) {
    if (DEBUG) cat(file = stderr(), "output$coE_geneGrp_vio_plot:NULL\n")
    return(NULL)
  }
  if (.schnappsEnv$DEBUGSAVE) {
    save(file = "~/SCHNAPPsDebug/coE_geneGrp_vio_plot.RData", list = c(ls()))
  }
  # load(file="~/SCHNAPPsDebug/coE_geneGrp_vio_plot.RData")

  featureData <- rowData(scEx_log)
  retVal <- coE_geneGrp_vioFunc(
    genesin = geneListStr,
    projections = projections,
    scEx = scEx_log,
    featureData = featureData,
    minExpr = minExpr,
    dbCluster = projectionVar,
    coE_showPermutations = coE_showPermutations,
    sampCol = scols,
    ccols = ccols
  )
retVal
```


## SOM

The som as implemented in SCHNAPPs will cluster the genes and output genes that cluster with a target gene. This makes sense when looking a given dbCluster and try to identify co-expressed genes. 
Here, we go through all the clusters and print out those groups of genes

```{r}
suppressMessages(require(kohonen))
suppressMessages(require(Rsomoclu))
iData = as.matrix(assays(scEx_log)[[1]])
geneName = "ENSG00000073861"
nSom = 20
featureData = rowData(scEx_log)
for (dbCl in levels(projections$dbCluster)) {
cols2use <- which(projections$dbCluster == dbCl)
  res2 <- Rsomoclu.train(
    input_data = iData[, cols2use],
    nSomX = nSom, nSomY = nSom,
    nEpoch = 10,
    radius0 = 0,
    radiusN = 0,
    radiusCooling = "linear",
    mapType = "planar",
    gridType = "rectangular",
    scale0 = 1,
    scaleN = 0.01,
    scaleCooling = "linear"
  )
  colnames(res2$codebook) <- colnames(iData)[cols2use]
  rownames(res2$globalBmus) <- make.unique(as.character(rownames(iData)), sep = "___")
  simGenes <- rownames(res2$globalBmus)[which(res2$globalBmus[, 1] == res2$globalBmus[geneName, 1] &
                                                res2$globalBmus[, 2] == res2$globalBmus[geneName, 2])]
  print(paste("dbCluster:", dbCl))
  print(featureData[simGenes,"symbol"])
}
```

## custom DGE


```{r}
myDiffExpFunctions <- list(
  c("Chi-square test of an estimated binomial distribution", "sCA_dge_CellViewfunc"),
  c("t-test", "sCA_dge_ttest"),
  c("DESeq2", "sCA_dge_deseq2"),
  c("seurat:wilcox", "sCA_dge_s_wilcox"),
  c("seurat:bimod", "sCA_dge_s_bimod"),
  c("seurat:t-test", "sCA_dge_s_t"),
  c("seurat:LR", "sCA_dge_s_LR"),
  c("seurat:neg-binomial", "sCA_dge_s_negbinom"),
  c("seurat:Poisson", "sCA_dge_s_poisson")
)

dgeFunc = myDiffExpFunctions[[1]][2]
if (dgeFunc %in% c("sCA_dge_deseq2", "sCA_dge_s_negbinom", "sCA_dge_s_poisson")) {
  scEx_log = scEx
}

# add projections
# c1 = c("AAAGATGTCTACCTGC-1", "AAAGCAATCTGCGACG-1", "AACACGTTCGTACCGG-1", "AACCGCGAGCAGGCTA-1")
projections$lung = projections$sampleNames %in% c("d3_lung", "d4_lung", "d8_lung", "d16_lung")

clusterNr = 12
c1 = rownames(projections[projections$dbCluster == clusterNr & projections$lung,])
c2 = rownames(projections[projections$dbCluster == clusterNr & ! projections$lung,])

top.genes <- do.call(dgeFunc, args = list(
  scEx_log = scEx_log,
  cells.1 = c1, cells.2 = c2
))
featureData <- rowData(scEx)

top.genes$symbol <-
  featureData[rownames(top.genes), "symbol"]
if ("Description" %in% colnames(featureData)) {
  top.genes$Description <- featureData[rownames(top.genes), "Description"]
}
rownames(top.genes) <- make.unique(as.character(top.genes$symbol), sep = "___")

DT::datatable(top.genes)
```

