---
title: "child report"
output: html_document
---

# General QC



```{r bj-gQC-setup, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, include=FALSE}
if(exists("params")){
  cat(file = stderr(), paste("Scater Plot report\n"))
}else{
  rm(list = ls())
  load("~/SCHNAPPsDebug/report.RData")
  cat(file=stderr(), getwd())
  
  require(shiny)
  require(plotly)
  require(shinythemes)
  require(ggplot2)
  require(DT)
  require(pheatmap)
  require(threejs)
  require(sm)
  require(RColorBrewer)
  require(mclust)
  require(reshape2)
  # require(cellrangerRkit)
  # require(SCORPIUS)
  require(ggplot2)
  require(knitr)
  require(kableExtra)
  require(shinyWidgets)
  require(scater)
  
  source("../../../serverFunctions.R")
  source("../../../reactives.R", local = TRUE)
  source("reactives.R", local = TRUE)
  
  LOCALEXECUTION = TRUE # to know that we are debugging.
  useCells = useCellsFunc(dataTables, 
                          geneNames = input$minExpGenes,
                          rmCells = input$cellsFiltersOut,
                          rmPattern = input$cellPatternRM,
                          keepCells = input$cellKeep,
                          cellKeepOnly = input$cellKeepOnly)
  
  geneSelectionValues <- geneSelectionValues()
  ipIDs = input$selectIds
  geneListSelection = input$geneListSelection
  minGene <- input$minGenesGS
  
  
  useGenes = useGenesFunc(dataTables, useCells, ipIDs, geneListSelection, minGene)
  featureDataReact = dataTables$featuredata[useGenes, ]
  featureData = dataTables$featuredata[useGenes, ]
  scEx = dataTables$scEx[useGenes, useCells]
  scEx_log = dataTables$scEx_log[useGenes, useCells]
  log2cpm = dataTables$log2cpm[useGenes, useCells]
  if(DEBUG)cat(file=stderr(), "pca\n")
  
  pca = pcaFunc(scEx_log, input$pcaRank, input$pcaCenter, input$pcaScale)
  if(DEBUG)cat(file=stderr(), "tsne\n")
  seed=1
  set.seed(seed = seed)
  tsne = run_tsne(pca, dims = 3, perplexity = 30, theta = 0.5)
  if(DEBUG)cat(file=stderr(), "tsne: done\n")
  if(DEBUG)cat(file=stderr(), "tsne.data\n")
  
  if(DEBUG)cat(file=stderr(), "scran_Cluster\n")
  clustering=list()
  
  kNr = 10
  for(kNr in 2:10) {
    set.seed(seed = seed)
    km = run_kmeans_clustering(pca, k=kNr)
    clustering[[paste0("kmeans_",kNr,"_clusters")]] = data.frame("Barcode" = rownames(data.frame(km$cluster)), "Cluster" = km$cluster)
  }
  
  scran_Cluster = clustering
  if(DEBUG)cat(file=stderr(), "scran_Cluster:done\n")
  
  
  tsne.data = data.frame(tsne$Y)
  colnames(tsne.data) = c("tsne1", "tsne2", "tsne3")
  # tsne.data$dbCluster = clustering$kmeans_10_clusters$Cluster-1
  tsne.data$dbCluster = clustering$kmeans_10_clusters$Cluster
  rownames(tsne.data) = clustering$kmeans_10_clusters$Barcode
  if(DEBUG)cat(file=stderr(), "tsne.data: done\n")
  
}


```




```{r bj-gQC-tsne3d, eval=FALSE, echo=TRUE}
# TODO: not working because tsne.data is not available
# cat(file=stderr(),paste("bj-gQC-tsne3d: ", class(tsne.data)))

tsne.data <- as.data.frame(tsne)
cat(file=stderr(),colnames(tsne.data)[1:5])
tsne.data$dbCluster <- as.factor(projections$dbCluster)

p <-
  plotly::plot_ly(
    tsne.data,
    x = ~ tsne1,
    y = ~ tsne2,
    z = ~ tsne3,
    type = "scatter3d",
    color =  ~ dbCluster,
    hoverinfo = "text",
    text = paste('Cluster:', as.numeric(as.character(tsne.data$dbCluster))),
    mode = 'markers',
    marker =
      list(
        line = list(width = 0),
        size = rep(10, nrow(tsne.data)),
        sizeref = 3
      )
  )
if(DEBUG)cat(file=stderr(), "output$gQC_tsne_main: done\n")
layout(p)



```

## UMI histogram


```{r gQC_plotUmiHist, eval=TRUE, echo=TRUE}

dat <- data.frame(counts = Matrix::colSums(assays(scEx)[["counts"]]))
dat$sample <- colData(scEx)$sampleNames
ggplot(data = dat, aes(counts, fill = sample)) +
  geom_histogram(bins = 50) +
  labs(title = "Histogram for raw counts", x = "count", y = "Frequency") +
  scale_fill_manual(values = scols, aesthetics = "fill")

```

## Histogram of samples


```{r histSamples, eval=TRUE, echo=TRUE}
sampleInf <- sampleInfoFunc(scEx)
scols = sampleCols$colPal
ccols <- clusterCols$colPal

gQC_sampleHistFunc(sampleInf, scols)
```

## Variances of PCs

```{r gQC_variancePCA, eval=TRUE, echo=TRUE}
# if(exists("pca$var_pcs")){
barplot(pca$var_pcs, main="Variance captured by first PCs")
# }
```


## TSNE plot

gQC_tsneDim : `r input$gQC_tsneDim`

gQC_tsnePerplexity : `r input$gQC_tsnePerplexity`

gQC_tsneTheta : `r input$gQC_tsneTheta`

gQC_tsneSeed : `r input$gQC_tsneSeed`

dimX : `r input$gQC_dim3D_x`

dimY : `r input$gQC_dim3D_y`

dimZ : `r input$gQC_dim3D_z`

dimCol : `r input$gQC_col3D`


```{r bj-GC-tsne, echo=TRUE}


dimX = input$gQC_dim3D_x
dimY = input$gQC_dim3D_y
dimZ = input$gQC_dim3D_z
dimCol = input$gQC_col3D


projections$dbCluster <- as.factor(projections$dbCluster)

tsnePlot(projections, dimX, dimY, dimZ, dimCol, scols, ccols)
```

## Projections table

```{r savegqcProj, echo=TRUE}

# save full table in tmp folder to be included in report
write.csv(projections, file = paste0(reportTempDir, "/gqcProjections.csv"))

```

Full table can be found here: [gqcProjections.csv](gqcProjections.csv)

## UMAP

myseed : `r input$gQC_um_randSeed`

runUMAP : `r input$activateUMAP`

n_neighbors : `r as.numeric(input$gQC_um_n_neighbors)`

n_components : `r as.numeric(input$gQC_um_n_components)`

n_epochs : `r as.numeric(input$gQC_um_n_epochs)`

alpha : `r as.numeric(input$um_alpha)`

init : `r input$gQC_um_init`

min_dist : `r as.numeric(input$gQC_um_min_dist)`

set_op_mix_ratio : `r as.numeric(input$gQC_um_set_op_mix_ratio)`

local_connectivity : `r as.numeric(input$gQC_um_local_connectivity)`

bandwidth : `r as.numeric(input$gQC_um_bandwidth)`

gamma : `r as.numeric(input$um_gamma)`

negative_sample_rate : `r as.numeric(input$gQC_um_negative_sample_rate)`

metric : `r input$gQC_um_metric`

spread : `r as.numeric(input$gQC_um_spread)`

dimY : `r input$"gQC_umap_main-dimension_y"`

dimX : `r input$"gQC_umap_main-dimension_x"`

dimCol : `r input$"gQC_umap_main-dimension_col"`

clId : `r input$"gQC_umap_main-clusters"`

geneNames : `r input$"gQC_umap_main-geneIds"`

geneNames2 : `r input$"gQC_umap_main-geneIds2"`

logx : `r input$"gQC_umap_main-logX"`

logy : `r input$"gQC_umap_main-logY"`

divXBy : `r input$"gQC_umap_main-devideXBy"`

divYBy : `r input$"gQC_umap_main-devideYBy"`

scols : `r sampleCols$colPal`

ccols : `r clusterCols$colPal`



```{r gqc_UMAP, echo=TRUE}
DEBUGSAVE <- FALSE
grpNs <- groupNames$namesDF
grpN <- make.names(input$groupName)

dimY <- input$"gQC_umap_main-dimension_y"
dimX <- input$"gQC_umap_main-dimension_x"
dimCol <- input$"gQC_umap_main-dimension_col"
clId <- input$"gQC_umap_main-clusters"
g_id <- featureData$symbol
geneNames <- input$"gQC_umap_main-geneIds"
geneNames2 <- input$"gQC_umap_main-geneIds2"
logx <- input$"gQC_umap_main-logX"
logy <- input$"gQC_umap_main-logY"
divXBy <- input$"gQC_umap_main-devideXBy"
divYBy <- input$"gQC_umap_main-devideYBy"
scols <- sampleCols$colPal
ccols <- clusterCols$colPal
legend.position <- "none"
if (is.null(divXBy)) divXBy <- "None"
if (is.null(divYBy)) divYBy <- "None"
if (is.null(logx)) {logx=FALSE}
if (is.null(logy)) {logy=FALSE}
projections <- updateProjectionsWithUmiCount(
  dimX = dimX, dimY = dimY,
  geneNames = geneNames,
  geneNames2 = geneNames2,
  scEx = scEx_log, projections = projections
)
if (dimCol == "sampleNames") {
  myColors <- scols
} else {
  myColors <- NULL
}
if (dimCol == "dbCluster") {
  myColors <- ccols
}

# if (all(c("UMAP1", "UMAP2") %in% colnames(projections))) {
  p1 <- plot2Dprojection(scEx_log, projections, g_id, featureData, geneNames,
                         geneNames2, dimX, dimY, clId, grpN, legend.position,
                         grpNs = grpNs, logx, logy, divXBy, divYBy, dimCol, colors = myColors
  )
  p1
# }
```




