### summary stats on input data

```{r, eval=FALSE}
cat(file = stderr(), paste(anovaName, "\n"))
```


#### number of umis per sample

```{r, eval=FALSE}
table(projections$sampleNames)
```

#### number umis per organ (lung = TRUE)

```{r, eval=FALSE}
table(projections$lung)
```


### full table


```{R, eval=FALSE}

rData <- rowData(inputData)
cellMeta <- colData(inputData)
meta.data <- cellMeta[, "sampleNames", drop = FALSE]
meta.data$organ <- "kidney"
meta.data$organ[projections$lung] <- "lung"
meta.data$organ <- as.factor(meta.data$organ)
# DT::datatable(as.data.frame(meta.data))


mat <- as.matrix(assays(inputData)[[1]])
aov2Results <- data.frame()
for (midx in 1:nrow(mat)) {
  m1 <- data.frame(expr = mat[midx, ], organ = meta.data$organ, sample = meta.data$sampleNames)
  res.aov2 <- aov(expr ~ organ + sample, data = m1)
  res <- summary(res.aov2)
  sumRes <- as.data.frame(res[[1]]["organ", ])
  rownames(sumRes) <- rownames(mat)[midx]
  sumRes$coef <- res.aov2$coefficients[["organlung"]]
  aov2Results <- rbind(aov2Results, sumRes)
}
aov2Results <- cbind(rData[rownames(aov2Results), c("symbol", "Description")], aov2Results)
aov2Results$ensg <- rownames(aov2Results)
rownames(aov2Results) <- aov2Results$symbol
DT::datatable(as.data.frame(aov2Results[!is.na(aov2Results$`F value`), ]))

```


### table genes of interest

```{r, eval=FALSE}
tmp = aov2Results[intGenes, ]
intGenes[is.na(tmp$symbol)]
tmp = tmp[!is.na(tmp$symbol),]
# tmp[11:15,]
intGTable <- as.data.frame(tmp)
DT::datatable(intGTable)

pValIntGenes[,anovaName] = intGTable[rownames(pValIntGenes), "Pr..F."]

```



### Panel plot samples/count (gene of interest)

```{r,fig.height=60, fig.width=12, eval=FALSE}
  .schnappsEnv <- new.env(parent=emptyenv())

source("~/Rstudio/Schnapps/inst/app/contributions/DE_DataExploration/reactives.R")
# panelplotFunc ----
# scEx_log singlecell Experiment object
# projections as used in schnapps
# genesin gene names to be plotted
# dimx4, dimy4 dimensions to be plotted on
# sameScale True/False
# nCol number of columns for final plot
# sampdes header for plot
# cellNs cell names to be used


retVal = panelPlotFunc(inputData, projections, intGenes, "sampleNames", "UMI.count", FALSE, 4, "all samples", rownames(projections)) 

retVal

```

### Panel plot lung/count (gene of interest)

```{r,fig.height=60, fig.width=12, eval=FALSE}
retVal = panelPlotFunc(inputData, projections, intGenes, "lung", "UMI.count", FALSE, 4, "lung/kidney", colnames(inputData)) 
retVal
```


### Panel plot samples/count (best)

Interesting genes defined as having a sum of squares >2 and a Pr(>F) < 0.05

```{r, eval=FALSE}
interestingRes = aov2Results[aov2Results$`Sum Sq`>2 & aov2Results$`Pr(>F)`<0.05,]
DT::datatable(as.data.frame(interestingRes))
```


```{r, eval=FALSE}
genesIn = rownames(interestingRes)[order(interestingRes$`Pr(>F)`,na.last = T,decreasing = F)[1:18]]
tmp = t(apply(assays(inputData[interestingRes[genesIn,"ensg"],])[[1]],1,FUN = function(x) {table(projections[which(x>0),"lung"])}))
rownames(tmp) = featureData[rownames(tmp), "symbol"]
colnames(tmp) = c("lung", "kidney")
DT::datatable(tmp, caption = "Table of genes which are 'significant' and how many cells expressing that gene  per organ")
```

```{r, eval=FALSE}
tmp = t(apply(assays(inputData[interestingRes[genesIn,"ensg"],])[[1]],1,FUN = function(x) {table(projections[which(x>0),"sampleNames"])}))
rownames(tmp) = featureData[rownames(tmp), "symbol"]
# colnames(tmp) = c("lung", "kidney")
DT::datatable(tmp, caption = "Table of genes which are 'significant' and how many cells expressing that gene  per sample")

```



```{r,fig.height=18, fig.width=12, eval=FALSE}


retVal = panelPlotFunc(inputData, projections, genesIn, "sampleNames", "UMI.count", FALSE, 3, "best 9 genes all samples", rownames(projections)) 

retVal

```

### Panel plot lung/count (best)

```{r,fig.height=18, fig.width=12, eval=FALSE}
retVal = panelPlotFunc(inputData, projections, genesIn, "lung", "UMI.count", FALSE, 3, "best 9 genes lung/kidney", colnames(inputData)) 
retVal
```

### Panel plot UMAP1/2 (best)

```{r,fig.height=18, fig.width=12, eval=FALSE}

if ("UMAP1" %in% colnames(projections)) {
  retVal = panelPlotFunc(inputData, projections, genesIn, "UMAP1", "UMAP2", FALSE, 3, "best genes ", colnames(inputData)) 
} else {
  retVal = panelPlotFunc(inputData, projections, genesIn, "tsne1", "tsne2", FALSE, 3, "best genes ", colnames(inputData)) 
}
retVal
```

### Panel plot PC1/2 (best)

```{r,fig.height=18, fig.width=12, eval=FALSE}
retVal = panelPlotFunc(inputData, projections, genesIn, "PC1", "PC2", FALSE, 3, "best  genes ", colnames(inputData)) 
retVal
```


