---
title: "child report"
output: html_document
---

# Data exploration

```{r bj-DE-setup, echo=TRUE, warning=FALSE}
if(exists("params")){
  cat(file=stderr(), paste("Scater Plot report\n"))
}else{
  rm(list = ls())
  load("~/SCHNAPPsDebug/report.RData")
  cat(file=stderr(), getwd())
  
  require(shiny)
  require(plotly)
  require(shinythemes)
  require(ggplot2)
  require(DT)
  require(pheatmap)
  require(threejs)
  require(sm)
  require(RColorBrewer)
  require(mclust)
  require(reshape2)
  # require(cellrangerRkit)
  # require(SCORPIUS)
  require(ggplot2)
  require(knitr)
  require(kableExtra)
  require(shinyWidgets)
  require(scater)
  
  source("../../../serverFunctions.R")
  source("../../../reactives.R", local = TRUE)
  # source("reactives.R", local = TRUE)
  
  LOCALEXECUTION = TRUE # to know that we are debugging.
  useCells = useCellsFunc(dataTables, 
                          geneNames = input$minExpGenes,
                          rmCells = input$cellsFiltersOut,
                          rmPattern = input$cellPatternRM,
                          keepCells = input$cellKeep,
                          cellKeepOnly = input$cellKeepOnly)
  ipIDs = input$selectIds
  geneListSelection = input$geneListSelection
  minGene <- input$minGenesGS
  
  useGenes = useGenesFunc(dataTables, useCells, ipIDs, geneListSelection, minGene)
  featureDataReact = dataTables$featuredata[useGenes, ]
  featureData = dataTables$featuredata[useGenes, ]
  scEx = assays(dataTables$scEx)[[1]][useGenes, useCells]
  scEx_log = assays(dataTables$scEx_log)[[1]][useGenes, useCells]
  log2cpm = dataTables$log2cpm[useGenes, useCells]
  
}
```


## normalization

Normalization method used: `r input$normalizationRadioButton` used.


`r input$scaterGeneList`

`r input$scaterGeneListRM`


## Expression

### 3D TSNE plot

```{r bj-DE-DE_tsne_plt, eval=TRUE, echo=TRUE}

  g_id <- input$DE_gene_id

 DE_dataExpltSNEPlot(scEx_log, g_id, projections)

```


### 2D 

2D plot 

g_id <- `r input$DE_gene_id`

geneNames <- `r input$"DE_expclusters-geneIds"`

clId <- `r input$"DE_expclusters-clusters"`

dimX <- `r input$"DE_expclusters-dimension_x"`

dimY <- `r input$"DE_expclusters-dimension_y"`


```{r bj-DE-2Dprojection, echo=TRUE, eval=TRUE}

data2plot = projections
gene_id <- input$DE_gene_id
moduleName = "DE_expclusters"

p2 <- twoDplotFromModule(twoDData = data2plot, moduleName = moduleName, input = input, projections = projections, g_id = gene_id) 

# TODO selected cells

p2

```



### VIOLIN PLOT 

```{r bj-DE-DE_gene_vio_plot, eval=TRUE, echo=TRUE}

  g_id <- input$DE_gene_id
  ccols <- clusterCols$colPal

  p1 <- DE_geneViolinFunc(scEx_log, g_id, projections, ccols)
p1

```

## Panel plot
output$DE_panelPlot <- renderPlot({

input$DE_clusterSelectionPanelPlot : `r input$DE_clusterSelectionPanelPlot`

input$DE_panelplotids : `r input$DE_panelplotids`

input$DE_dim_x : `r input$DE_dim_x`

input$DE_dim_y : `r input$DE_dim_y`

```{r bj-DE-DE_panelPlot, eval=TRUE, echo=TRUE}

  genesin <- input$DE_panelplotids
  cl4 <- input$DE_clusterSelectionPanelPlot
  dimx4 <- input$DE_dim_x
  dimy4 <- input$DE_dim_y

  genesin <- toupper(genesin)
  genesin <- gsub(" ", "", genesin, fixed = TRUE)
  genesin <- strsplit(genesin, ",")
  genesin <- genesin[[1]]
 
  featureData <- rowData(scEx_log)
  featureData$symbol = toupper(featureData$symbol)
  genesin <- genesin[which(genesin %in% featureData$symbol)]
if (length(genesin) > 0) {
  par(mfrow = c(ceiling(length(genesin) / 4), 4), mai = c(0., .3, .3, .3))
  rbPal <- colorRampPalette(c("#f0f0f0", "red"))
  ylim <- c(min(projections[, dimy4]), max(projections[, dimy4]))
  if (class(projections[, dimx4]) == "factor" & dimy4 == "UMI.count") {
    ymax <- 0
    for (i in 1:length(genesin)) {
      geneIdx <- which(featureData$symbol == genesin[i])
      ymax <- max(ymax, max(Matrix::colSums(assays(scEx_log)[["logcounts"]][geneIdx, , drop = FALSE])))
    }
    ylim <- c(0, ymax)
  }
  if (cl4 == "All") {
    for (i in 1:length(genesin)) {
      geneIdx <- which(featureData$symbol == genesin[i])
      Col <- rbPal(10)[
        as.numeric(
          cut(
            as.numeric(
              assays(scEx_log)[[1]][
                rownames(featureData[geneIdx, ]),
              ]
            ),
            breaks = 10
          )
        )
      ]
      if (class(projections[, dimx4]) == "factor" & dimy4 == "UMI.count") {
        projections[, dimy4] <- Matrix::colSums(assays(scEx_log)[["logcounts"]][geneIdx, , drop = FALSE])
      }

      plot(projections[, dimx4], projections[, dimy4],
        col = Col, pch = 16, frame.plot = TRUE, ann = FALSE, ylim = ylim
      )
      title(genesin[i], line = -1.2, adj = 0.05, cex.main = 2)
      if (DEBUG) cat(file = stderr(), genesin[i])
    }
  } else {
    for (i in 1:length(genesin)) {
      geneIdx <- which(featureData$symbol == genesin[i])
      subsetTSNE <- subset(projections, dbCluster == cl4)

      Col <- rbPal(10)[
        as.numeric(
          cut(
            as.numeric(
              assays(scEx_log)[[1]][
                rownames(featureData[geneIdx, ]),
              ]
            ),
            breaks = 10
          )
        )
      ]

      names(Col) <- rownames(projections)
      plotCol <- Col[rownames(subsetTSNE)]
      if (class(projections[, dimx4]) == "factor" & dimy4 == "UMI.count") {
        projections[, dimy4] <- Matrix::colSums(assays(scEx_log)[["logcounts"]][geneIdx, , drop = FALSE])
        subsetTSNE <- subset(projections, dbCluster == cl4)
      }

      plot(subsetTSNE[, dimx4], subsetTSNE[, dimy4],
        col = plotCol, pch = 16, frame.plot = TRUE,
        ann = FALSE, ylim = ylim
      )
      title(genesin[i], line = -1.2, adj = 0.05, cex.main = 2)
      if (DEBUG) cat(file = stderr(), cl4)
    }
  }
  
}
```



## scater QC

```{r bj-DE-scater, eval=TRUE, echo=TRUE, warning=FALSE }
library(png)
img=DE_scaterPNG
if (file.exists(img$src))
  include_graphics(img$src)

```



