---
title: "coExpression"
author: "Bernd Jagla"
date: "3/23/2018"
output: html_document
  code_folding: hide
---

# Co-expression

```{r bj-coExp-setup, echo=TRUE, warning=FALSE}
library(magrittr)
if (exists("params")) {
  cat(file = stderr(), paste("Scater Plot report\n"))
} else {
  rm(list = ls())
  load("~/SCHNAPPsDebug/report.RData")
  cat(file = stderr(), getwd())
  
library(magrittr)
  require(shiny)
  require(plotly)
  require(shinythemes)
  require(ggplot2)
  require(DT)
  require(pheatmap)
  require(threejs)
  require(sm)
  require(RColorBrewer)
  require(mclust)
  require(reshape2)
  # require(cellrangerRkit)
  # require(SCORPIUS)
  require(ggplot2)
  require(knitr)
  require(kableExtra)
  require(shinyWidgets)
  require(scater)
  
  source("../../../serverFunctions.R")
  source("../../../reactives.R", local = TRUE)
  # source("reactives.R", local = TRUE)
  
  LOCALEXECUTION <- TRUE # to know that we are debugging.
  useCells <- useCellsFunc(dataTables,
                           geneNames = input$minExpGenes,
                           rmCells = input$cellsFiltersOut,
                           rmPattern = input$cellPatternRM,
                           keepCells = input$cellKeep,
                           cellKeepOnly = input$cellKeepOnly
  )
  
  ipIDs <- input$selectIds
  geneListSelection <- input$geneListSelection
  minGene <- input$minGenesGS
  
  useGenes <- useGenesFunc(dataTables, useCells, ipIDs, geneListSelection, minGene)
  featureDataReact <- dataTables$featuredata[useGenes, ]
  featureData <- dataTables$featuredata[useGenes, ]
  scEx <- dataTables$scEx[useGenes, useCells]
  scEx_log <- dataTables$scEx_log[useGenes, useCells]
  log2cpm <- dataTables$log2cpm[useGenes, useCells]
}
```

## All clusters 

### Heatmap

genesin : `r input$coE_heatmap_geneids`

sampCol : `r sampleCols$colPal`

ccols : `r clusterCols$colPal`


```{r coExpHeatmapModule}
genesin <- input$coE_heatmap_geneids
sampCol <- sampleCols$colPal
ccols <- clusterCols$colPal


scEx_matrix <- as.matrix(assays(scEx_log)[["logcounts"]])
heatmapData <- coE_heatmapFunc(
  featureData = featureData, scEx_matrix = scEx_matrix,
  projections = projections, genesin = genesin, cells = colnames(scEx_matrix),
  sampCol = sampCol, ccols = ccols
)

if (nrow(heatmapData$mat)>0){
  moduleName <- "coExpHeatmapModule"
  heatmapPlotFromModule(heatmapData, moduleName, input, projections)
}
```



## Selected

### 2D plot with selection of cells 

clId <- `r input$"coE_selected-clusters"`

dimX <- `r input$"coE_selected-dimension_x"`

dimY <- `r input$"coE_selected-dimension_y"`



```{r selectd2D, echo=TRUE, eval=TRUE, warning=FALSE}

DEBUGSAVE <- FALSE
grpNs <- groupNames$namesDF
grpN <- make.names(input$groupName)

dimY <- input$"coE_selected-dimension_y"
dimX <- input$"coE_selected-dimension_x"
dimCol <- input$"coE_selected-dimension_col"
clId <- input$"coE_selected-clusters"
g_id <- NULL
geneNames <- input$"coE_selected-geneIds"
geneNames2 <- input$"coE_selected-geneIds2"
logx <- input$"coE_selected-logX"
logy <- input$"coE_selected-logY"
divXBy <- input$"coE_selected-devideXBy"
divYBy <- input$"coE_selected-devideYBy"
scols <- sampleCols$colPal
ccols <- clusterCols$colPal
legend.position <- "none"
scCells <- `coE_selctedCluster-selectedCells`

if (is.null(scEx_log) | is.null(scEx_log) | is.null(projections)) {
  if (DEBUG) cat(file = stderr(), paste("output$clusterPlot:NULL\n"))
  return(NULL)
}

featureData <- rowData(scEx_log)

# load(file=paste0("~/SCHNAPPsDebug/clusterPlot", "ns", ".RData", collapse = "."))
if (is.null(g_id) || nchar(g_id) == 0) {
  g_id <- featureData$symbol
}
if (is.null(logx)) logx <- FALSE
if (is.null(logy)) logy <- FALSE
if (is.null(divXBy)) divXBy <- "None"
if (is.null(divYBy)) divYBy <- "None"

subsetData <- updateProjectionsWithUmiCount(
  dimX = dimX, dimY = dimY,
  geneNames = geneNames,
  geneNames2 = geneNames2,
  scEx = scEx_log, projections = projections
)
if (dimCol == "sampleNames") {
  myColors <- scols
} else {
  myColors <- NULL
}
if (dimCol == "dbCluster") {
  myColors <- ccols
}

p1 <- plot2Dprojection(scEx_log, projections, g_id, featureData, geneNames,
                       geneNames2, dimX, dimY, clId, grpN, legend.position,
                       grpNs = grpNs, logx, logy, divXBy, divYBy, dimCol, colors = myColors
)


if (!is.null(p1)){
  p1 %>%
    add_trace(
      data = subsetData[scCells, ],
      x =
        ~ get(dimX), y = ~ get(dimY),
      type = "scatter", mode =
        "markers", color = "red",
      name =
        "selected", showlegend = TRUE,
      inherit = F
    )
}

```


#### Heatmap selected

callModule(
pHeatMapModule, 
"coE_heatmapSelectedModule", 
coE_heatmapSelectedReactive
)

coE_heatmapselected_geneids `r input$coE_heatmapselected_geneids`

'selected-geneIds' `r input$'coE_selected-geneIds'`

'selected-clusters' `r input$'coE_selected-clusters'`

'coE_heatmapSelectedModule-ColNames' `r input$'coE_heatmapSelectedModule-ColNames'`

orderColNames : `r input$'coE_heatmapSelectedModule-orderNames'`

moreOptions <- `r input$'coE_heatmapSelectedModule-moreOptions'`


```{r coE_heatmapSelectedModule, echo=TRUE, eval=TRUE}
# save(file = "~/SCHNAPPsDebug/selectedHeatmap.1.RData", list = c(ls(), ls(envir = globalenv())))
genesin <- input$coE_heatmapselected_geneids

# get selected cells
scCells <- `coE_selctedCluster-selectedCells`

# brushedPs <- input$"coE_selected-b1"
# geneNames <- input$'coE_selected-geneIds'
inpClusters <- input$"coE_selected-clusters"
# dimX <- brushedPs$mapping$x
# dimY <- brushedPs$mapping$y
sampCol <- sampleCols$colPal
ccols <- clusterCols$colPal


# geneid <- geneName2Index(geneNames, featureData)
projections <- updateProjectionsWithUmiCount(
  dimX = dimX, dimY = dimY,
  geneNames = geneNames,
  scEx = scEx_log, projections = projections
)

subsetData <- subset(projections, dbCluster %in% inpClusters)
# cells.names <- shiny::brushedPoints(subsetData, brushedPs)

# cells.1 <- rownames(scCells)
heatmapData <- coE_heatmapFunc(featureData,
                               scEx_matrix,
                               projections,
                               genesin,
                               cells = scCells,
                               sampCol = sampCol,
                               ccols = ccols
)



moduleName <- "coE_heatmapSelectedModule"
heatmapPlotFromModule(heatmapData, moduleName, input, projections)
```

#### table of genes that have at least `r input$coEtgMinExpr` UMIs in `r input$coEtgPerc`% of the selected cells

```{r topexpCells, echo=TRUE, eval=TRUE}


coEtgPerc <- input$coEtgPerc
coEtgminExpr <- input$coEtgMinExpr
scCells <- `coE_selctedCluster-selectedCells`

if (is.null(scEx_log) || is.null(scCells)) {
  
} else {
  
  
  
  featureData <- rowData(scEx_log)
  # we only work on cells that have been selected
  mat <- assays(scEx_log)[[1]][, scCells]
  # only genes that express at least coEtgminExpr UMIs
  mat[mat < coEtgminExpr] <- 0
  # only genes that are expressed in coEtgPerc or more cells
  allexpressed <- Matrix::rowSums(mat > 0) / length(scCells) * 100 >= coEtgPerc
  mat <- mat[allexpressed, ]
  
  cv <- function(x) {
    sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
  }
  matCV <- apply(mat, 1, cv)
  # top.genes <- as.data.frame(exprs(scEx_log))
  maxRows <- min(nrow(mat), 200)
  top.genesOrder <- order(matCV, decreasing = TRUE)[1:maxRows]
  dataTables <- NULL
  if (dim(mat)[1] > 0) {
    mat <- mat[top.genesOrder, ]
    fd <- featureData[rownames(mat), c("symbol", "Description")]
    matCV <- matCV[rownames(mat)]
    fd <- cbind(fd, matCV)
    colnames(fd) <- c("gene", "description", "CV")
    # since we are returning a table to be plotted, we convert to regular table (non-sparse)
    outMat <- cbind2(fd, as.matrix(mat))
    rownames(outMat) <- make.unique(as.character(outMat$gene), sep = "___")
    dataTables <- as.data.frame(outMat)
  }
  
  maxCol <- min(20, ncol(dataTables))
  if (dim(dataTables)[2] > 1) {
    DT::datatable(dataTables[, 1:maxCol],
                  rownames = F, filter = "top",
                  options = list(
                    orderClasses = TRUE,
                    autoWidth = TRUE
                  )
    )
  } else {
    print("no table to print")
  }
}
```

```{r saveTOPGENES, echo=TRUE, eval=TRUE}
# save full table in tmp folder to be included in report
if (is.data.frame(dataTables)) {
  write.csv(dataTables, file = paste0(reportTempDir, "/output_coE_topExpGenes.csv"))
}
```

Full table can be found here: [output_coE_topExpGenes.csv](output_coE_topExpGenes.csv)



## Violin plot coexpressed genes

geneListStr <- `r input$coE_geneGrpVioIds`

projectionVar <- `r input$coE_dimension_xVioiGrp`

minExpr <- `r input$coEminExpr`

```{r violinPlot, echo=TRUE, eval=TRUE}

geneListStr <- input$coE_geneGrpVioIds
projectionVar <- input$coE_dimension_xVioiGrp
minExpr <- input$coEminExpr
coE_showPermutations <- input$coE_showPermutations
# colPal = coE_geneGrp_vioFunc # TODO must be wrong
sampCol <- sampleCols$colPal
ccols <- clusterCols$colPal

if (is.null(projections)) {
  print("no violin plot to print")
} else {
  featureData <- rowData(scEx_log)
  retVal <- coE_geneGrp_vioFunc(
    genesin = geneListStr,
    projections = projections,
    scEx = scEx_log,
    featureData = featureData,
    minExpr = minExpr,
    dbCluster = projectionVar,
    coE_showPermutations = coE_showPermutations,
    sampCol = sampCol,
    ccols = ccols
  )
  retVal
}
```


## Self organizing map (SOM)

  genesin : `r input$coE_geneSOM`
  
  nSOM : `r input$coE_dimSOM`


```{r coe_som}
  genesin <- input$coE_geneSOM
  nSOM <- input$coE_dimSOM
  sampCol <- sampleCols$colPal
  ccols <- clusterCols$colPal

  scEx_matrix <- as.matrix(assays(scEx_log)[[1]])
  featureData <- rowData(scEx_log)
  # go from readable gene name to ENSG number
  genesin <- geneName2Index(genesin, featureData)

  geneNames <- coE_somFunction(iData = scEx_matrix, nSom = nSOM, geneName = genesin)

  annotation <- data.frame(projections[, c("dbCluster", "sampleNames")])
  rownames(annotation) <- rownames(projections)
  colnames(annotation) <- c("Cluster", "sampleNames")
  annCols <- list("sampleNames" = sampCol,
                  "Cluster" = ccols)
  
  retVal <- list(
    mat = scEx_matrix[geneNames, ,drop = FALSE],
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    # scale = "row",
    fontsize_row = 14,
    labels_row = featureData[geneNames, "symbol"],
    show_rownames = TRUE,
    annotation_col = annotation,
    show_colnames = FALSE,
    annotation_legend = TRUE,
    # breaks = seq(minBreak, maxBreak, by = stepBreak),
    # filename = 'test.png',
    # filename = normalizePath(outfile),
    color = colorRampPalette(rev(RColorBrewer::brewer.pal(
      n = 6, name =
        "RdBu"
    )))(6),
    annotation_colors = annCols
  )
  # system.time(do.call(TRONCO::pheatmap, retVal))


if (nrow(retVal$mat) > 1) {
  moduleName <- "coE_heatmapSOM"
  heatmapPlotFromModule(retVal, moduleName, input, projections)
}

```

*Genes found by SOM*:

`r paste(featureData[geneNames, "symbol"], collapse = ", ", sep = ",")`



